Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-24 Latex/tex/pr.tex
near to last

physical resources which contain RAM, Memory and CPU.
Let, the required resources for VNF $f$ in slice $s$ is represented by a three dimensional vector as follow

@@

    \includegraphics[width=\linewidth]{f11}

>>>>

physical resources that contain RAM, Memory, and CPU.
Let, the required resources for VNF $f$ in slice $s$ is represented by a three-dimensional vector as follow

@@

    \includegraphics[width=\linewidth]{f111}
